### 2024-01-11 inst/scripts/exploreNeutralTraits.Rmd
add mat mean and other

matmean <- function(m)Reduce("+",m)/length(m)

#sorry :D
lapply(lapply(rhodep,lapply,matmean),lapply,image,zlim=c(0,150),xlab="comu",x=c(1,2,3,4),y=c(1,2,3,4),ylab="traits")
```

@@

```{r,eval=F}
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
tstep=5000
repli=10
library(parallel)
neutraltraitsParam$s=c(0,0,1,1)
initcomus=initialiseCommunities(traits=initAdaptiveTraits(ki=ki,km=km,n=3),coordinates=random2Dgrid(K=ki+km,Gx=G),G=G,sizes=150,plot=T)

initcomus$adaptivetraits[1,]=c(1,1,1)
cl <- makeCluster(10,type="FORK")

rhos=c(0,1)
rhodepSBBIB=lapply(rhos,function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           #allinlaw=replicate(repli,
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)[-1,]
                                  #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                  do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

@@

stopCluster(cl)
saveRDS(file="precompSBbibi_adc.RDS",rhodepSBBIB)
```

@@

```{r}
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
tstep=2000
repli=50
library(parallel)
neutraltraitsParam$s=c(0,0,1,1)

initcomus$size=unname(table(population[,"community"]))
cl <- makeCluster(10,type="FORK")

rhos=c(0,.5,1)
rhodepSBBIB=lapply(rhos,function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           #allinlaw=replicate(repli,
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)[-1,]
                                  #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                  do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

           neutraltraitsParam$post[,"i"]=0
           neutraltraitsParam$post[,"h"]=1
           #allposthoriz=replicate(repli,{
           allposthoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                      quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                      pop=quickV$population
                                      #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)
                                      #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

           neutraltraitsParam$post[,"h"]=0
           neutraltraitsParam$pre[,"h"]=1
           #allprehoriz=replicate(repli,{
           allprehoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                     quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                     pop=quickV$population
                                     #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)
                                     #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

@@

stopCluster(cl)
saveRDS(file="precompSBbibi.RDS",rhodepSBBIB)
```

@@

par(mfrow=c(2,3))
for(rr in 1:2){
for(pth in 1:3){
plot(1,1,ylim=c(0,1),xlim=c(0,1000),pch="n")
sapply(rhodepSBBIB[[rr]][[pth]],function(olo)sapply(1:4,function(tr)lines(olo[,tr],col=tr)))
```

||||||| constructed merge base
=======
```{r}

>>>>

#sorry :D
lapply(lapply(rhodepSBBIB,lapply,matmean),lapply,image,zlim=c(0,150),xlab="comu",x=c(1,2,3,4),y=c(1,2,3,4),ylab="traits")
```

@@

```{r,eval=F}
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
tstep=5000
repli=50
library(parallel)
neutraltraitsParam$s=c(0,0,1,1)
initcomus=initialiseCommunities(traits=initAdaptiveTraits(ki=ki,km=km,n=3),coordinates=random2Dgrid(K=ki+km,Gx=G),G=G,sizes=150,plot=T)

initcomus$size=unname(table(population[,"community"]))
rhos=c(0,.5,1)
cl <- makeCluster(10,type="FORK")

rhodepHigherRandD=lapply(rhos,function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           #allinlaw=replicate(repli,
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.05, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
>>>>>>> Stashed changes
                                  pop=quickV$population
                                  #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)[-1,]
                                  #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                  do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

           neutraltraitsParam$post[,"i"]=0
           neutraltraitsParam$post[,"h"]=1
           #allposthoriz=replicate(repli,{
           allposthoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                      quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.05, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                      pop=quickV$population
                                      #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)
                                      #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

           neutraltraitsParam$post[,"h"]=0
           neutraltraitsParam$pre[,"h"]=1
           #allprehoriz=replicate(repli,{
           allprehoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                     quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.05, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                     pop=quickV$population
                                     #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)
                                     #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

@@

stopCluster(cl)
saveRDS(file="precompSB_neutr_rep50_ts2000.RDS",rhodepSBBIB)
```

@@

```{r}
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
tstep=10000
repli=5
library(parallel)
neutraltraitsParam$s=c(0,0,1,1)

initcomus=initialiseCommunities(traits=initAdaptiveTraits(ki=3,km=1,n=3),coordinates=random2Dgrid(K=ki+km,Gx=G),G=G,sizes=150,plot=T)
initcomus$size=unname(table(population[,"community"]))
cl <- makeCluster(10,type="FORK")

rhos=c(0,.5,1)
rhodepSBBIB=lapply(rhos,function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           #allinlaw=replicate(repli,
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.2, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)[-1,]
                                  #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                  do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

           neutraltraitsParam$post[,"i"]=0
           neutraltraitsParam$post[,"h"]=1
           #allposthoriz=replicate(repli,{
           allposthoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                      quickV=modelVector(K=K, m=1, b=0.2, r=0.2, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                      pop=quickV$population
                                      #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)
                                      #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

           neutraltraitsParam$post[,"h"]=0
           neutraltraitsParam$pre[,"h"]=1
           #allprehoriz=replicate(repli,{
           allprehoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                     quickV=modelVector(K=K, m=1, b=0.2, r=0.2, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                     pop=quickV$population
                                     #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)
                                     #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

@@

stopCluster(cl)
saveRDS(file="precompSB_50_2000ts.RDS",rhodepSBBIB)
```

@@

par(mfrow=c(3,3))
for(rr in 1:length(rhodepSBBIB)){
for(pth in 1:length(rhodepSBBIB[[rr]])){
plot(1,1,ylim=c(0,1),xlim=c(0,tstep),pch="n")
sapply(rhodepSBBIB[[rr]][[pth]],function(olo)sapply(1:4,function(tr)lines(olo[,tr],col=tr)))
```
